A higher order approximate static condensation method for multi-material diffusion problems

### 2019-01-25 num_sec.tex
Added flux results

\section{Numerical results}\label{sec:num}

@@

For the error~$e_h \coloneqq p - p_h$ between the exact and computed solutions we have
\begin{equation}\label{l2norm}
	\errlTwo{h} \coloneqq \| e_h \|_{\lTwoSpace} = \| p - p_h \|_{\lTwoSpace} = \| P_h\,p - P_h\,p_h \|_{\LTwoSpace} = \| P_h\,p - p_h \|_{\LTwoSpace}
\end{equation}
since~$P_h$ is linear and~$p_h \in \mathbb V_h$. The discrete norm~\eqref{l2norm} of the discretization error is computed as follows:
$$
	\errlTwo{h} = \left[\sum\limits_{\bcell \in \bmesh_h}\sum\limits_{\mcell\in\mmesh(\bcell)} \left(\frac{1}{|\mcell|}\int_{\mcell} p \diff{\vect x} - p_h(\mcell)\right)^2|\mcell|\right]^\frac12,
$$
where $|\mcell|$ is the area of cell $\mcell$.

@@

\begin{table}[h!]
	\centering
	\caption{Piecewise linear example: convergence \label{fig:conv:pwlin}}
	\footnotesize
	\begin{tabular}[1.5]{| c | c || c | c || c |}
		\hline
		\multirow{5}{*}{\rotatebox{90}{ASC(0)}} & $h$ & $\errlTwo{0}$ & $\rho$ & $\errInf{0}$ \\
		\cline{2-5}
		& $3.5\times10^{-1}$ & $7.3\times10^{-1}$ & & 4.8 \\
		\cline{2-5}
		& $8.8\times10^{-2}$ & $1.6\times10^{-1}$ & 1.1 & 1.2 \\
		\cline{2-5}
		& $2.2\times10^{-2}$ & $3.7\times10^{-2}$ & 1.1 & $3.4\times10^{-1}$ \\
		\cline{2-5}
		& $5.5\times10^{-3}$ & $8.9\times10^{-3}$ & 1.0 & $7.9\times10^{-2}$ \\
		\hline
		\hline
		\multirow{5}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{1}$ & $\rho$ & $\errInf{1}$ \\
		\cline{2-5}
		& $3.5\times10^{-1}$ & $2.5\times10^{-2}$ & & $1.6\times10^{-1}$ \\
		\cline{2-5}
		& $8.8\times10^{-2}$ & $1.9\times10^{-3}$ & 1.84 & $6.3\times10^{-2}$ \\
		\cline{2-5}
		& $2.2\times10^{-2}$ & $1.6\times10^{-4}$ & 1.79 & $9.8\times10^{-3}$ \\
		\cline{2-5}
		& $5.5\times10^{-3}$ & $1.3\times10^{-5}$ & 1.80 & $4.0\times10^{-3}$ \\
		\hline
	\end{tabular}
\end{table}

Numerical results are shown in Table~\ref{fig:conv:pwlin}. We observe that ASC(0) converges linearly with respect to the $\lTwo$-norm, and ASC(1) has the convergence rate close to quadratic with respect to the $\lTwo$-norm.

@@

\begin{table}[h!]
	\centering
	\caption{Piecewise quadratic example, two materials: convergence \label{tab:conv:pwquad2}}
	\footnotesize
	\begin{tabular}[1.1]{| c | c || c | c || c |}
		\hline
		\multirow{7}{*}{\rotatebox{90}{ASC(0)}} & $h$ & $\errlTwo{0}$ & ${\rho}$ & $\errInf{0}$ \\
		\cline{2-5}
		& $3.0\times10^{-1}$ & $2.4\times10^{-3}$ & & $6.3\times10^{-1}$ \\
		\cline{2-5}
		& $1.5\times10^{-1}$ & $6.5\times10^{-4}$ & 2.0 & $7.0\times10^{-3}$ \\
		\cline{2-5}
		& $8.1\times10^{-2}$ & $2.6\times10^{-4}$ & 1.4 & $3.2\times10^{-3}$ \\
		\cline{2-5}
		& $4.2\times10^{-2}$ & $1.4\times10^{-4}$ & 0.9 & $2.3\times10^{-3}$ \\
		\cline{2-5}
		& $2.1\times10^{-2}$ & $3.7\times10^{-5}$ & 1.9 & $1.1\times10^{-3}$ \\
		\cline{2-5}
		& $1.0\times10^{-2}$ & $2.7\times10^{-5}$ & 0.4 & $8.6\times10^{-4}$ \\
		\hline
	\end{tabular}
	\begin{tabular}[1.1]{| c | c || c | c || c |}
		\hline
		\multirow{7}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{1}$ & ${\rho}$ & $\errInf{1}$ \\
		\cline{2-5}
		& $3.0\times10^{-1}$ & $2.4\times10^{-3}$ & & $2.1\times10^{-3}$ \\
		\cline{2-5}
		& {$1.5\times10^{-1}$} & $7.0\times10^{-4}$ & 1.9 & {$1.3\times10^{-2}$} \\
		\cline{2-5}
		& $8.1\times10^{-2}$ & $2.3\times10^{-4}$ & 1.8 & $6.8\times10^{-4}$ \\
		\cline{2-5}
		& $4.2\times10^{-2}$ & $6.8\times10^{-5}$ & 1.8 & $3.2\times10^{-4}$ \\
		\cline{2-5}
		& $2.1\times10^{-2}$ & $2.0\times10^{-5}$ & 1.8 & $1.1\times10^{-4}$ \\
		\cline{2-5}
		& $1.0\times10^{-2}$ & $5.4\times10^{-6}$ & 1.9 & $3.3\times10^{-5}$ \\
		\hline
	\end{tabular}
\end{table}

The norms of the errors are shown in Table~\ref{tab:conv:pwquad2}. ASC(1) demonstrates convergence with the rate in the $\lTwo$-norm close to quadratic. ASC(0) convergence rate fluctuates significantly.

We also observe a bump in the max norm error for ASC(1) on the second mesh level, $h = 1.5\times10^{-1}$. To have some insight, we show the corresponding mesh in the Figure~\ref{fig:conv:pwquad2:inf:mesh}. One may note that the interface reconstruction produces significant discontinuity of interfaces: A small volume of the external material, i.e. the one occupying $\Omega_2$ domain, appears inside the disk (domain $\Omega_1$). Due to constant trace approximation, ASC(0) is not sensitive to such irregularity. It turns out that for ASC(1) the $\ell^\infty$ norm of the error is affected by the appearance of such small isolated cut cells. At the same time, this does not affect the $\lTwo$-convergence of ASC(1).

@@

>>>>

\section{Numerica results}\label{sec:num}

@@

For the error~$e_h \coloneqq p - p_h$ between the exact and computed solutions we have
\begin{equation}\label{l2norm}
	\errlTwo{h} \coloneqq \| e_h \|_{\lTwoSpace} = \| p - p_h \|_{\lTwoSpace} = \| P_h\,p - P_h\,p_h \|_{\LTwoSpace} = \| P_h\,p - p_h \|_{\LTwoSpace}
\end{equation}
since~$P_h$ is linear and~$p_h \in \mathbb V_h$. The discrete norm~\eqref{l2norm} of the concentration discretization error is computed as follows:
$$
	\errlTwo{h} = \left[\sum\limits_{\bcell \in \bmesh_h}\sum\limits_{\mcell\in\mmesh(\bcell)} \left(\frac{1}{|\mcell|}\int_{\mcell} p \diff{\vect x} - p_h(\mcell)\right)^2|\mcell|\right]^\frac12,
$$
        where $|\mcell|$ is the area of cell $\mcell$. While the disrete norm of the flux discretization error is defined as follows:
        $$
        \varepsilon_h^{l_2} =  \left[\sum\limits_{\bface \in \bmesh_h}
          A_\bface\left(
          \sum\limits_{\mface\in\bface}
          \frac{1}{|\mface|}\int_{\mface}
          \vect u \diff{\vect s}  - \sum\limits_{\mface\in\bface}\vect u_h(\mface)\right)^2 
          \right]^\frac12
        $$
        where $A_\bface|$ is the representative are of a face $\bface$ which is equal to the arithmetic average
of areas of cells sharing the face $\bface$.

@@

\begin{table}[h!]
	\centering
	\caption{Piecewise linear example: convergence \label{fig:conv:pwlin}}
	\footnotesize
	\begin{tabular}[1.5]{| c | c || c | c | c || c | c  ||}
		\hline
		\multirow{5}{*}{\rotatebox{90}{ASC(0)}} & $h$ & $\errlTwo{0}$ & $\rho_p$ & $\errInf{0}$
                                                              & $\varepsilon^{l_2}_0$ & $\rho_u$ \\              %& $\varepsilon^\infty_0$ \\
		\cline{2-7}
		& $3.5\times10^{-1}$ & $7.3\times10^{-1}$ &     & 4.8               & $ 6.6\times10^{-1}$ &  \\              %    & 7.9 \\
		\cline{2-7}
		& $8.8\times10^{-2}$ & $1.6\times10^{-1}$ & 1.1 & 1.2               & $ 3.5\times10^{-1}$ & 0.46 \\              %& 6.0\\
		\cline{2-7}
		& $2.2\times10^{-2}$ & $3.7\times10^{-2}$ & 1.1 & $3.4\times10^{-1}$ & $ 1.3\times10^{-1}$ & 0.71 \\              %& 5.8\\
		\cline{2-7}
		& $5.5\times10^{-3}$ & $8.9\times10^{-3}$ & 1.0 & $7.9\times10^{-2}$ & $ 4.1\times10^{-2}$ & 0.83 \\              %& 6.0\\
		\hline
		\hline
		\multirow{5}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{1}$ & $\rho$ & $\errInf{1}$
                & $\varepsilon^{l_2}_1$ & $\rho_u$ \\              %& $\varepsilon^\infty_1$\\
		\cline{2-7}
		& $3.5\times10^{-1}$ & $2.5\times10^{-2}$ & & $2.9\times10^{-1}$      & $ 4.6\times10^{-2}$ &   \\              %  &0.51\\
		\cline{2-7}
		& $8.8\times10^{-2}$ & $1.9\times10^{-3}$ & 1.84 & $6.6\times10^{-2}$ & $ 2.0\times10^{-2}$ & 0.6 \\              %&0.46\\
		\cline{2-7}
		& $2.2\times10^{-2}$ & $1.6\times10^{-4}$ & 1.79 & $4.3\times10^{-2}$ & $ 5.5\times10^{-3}$ & 0.93 \\              %&0.57\\
		\cline{2-7}
		& $5.5\times10^{-3}$ & $1.3\times10^{-5}$ & 1.80 & $2.0\times10^{-2}$ & $ 1.3\times10^{-3}$ & 1.   \\  %& 0.46\\
		\hline
	\end{tabular}
\end{table}

Numerical results are shown in Table~\ref{fig:conv:pwlin}. We observe that ASC(0) converges linearly with respect to the $\lTwo$-norm,
and ASC(1) has the convergence rate close to quadratic with respect to the $\lTwo$-norm.
The convergence of the flux errors is also is higher for ASC(1) method and is close to linear convergence.

@@

\begin{table}[h!]
	\centering
	\caption{Piecewise quadratic example, two materials: convergence \label{tab:conv:pwquad2}}
	\footnotesize
	\begin{tabular}[1.1]{| c | c || c | c | c ||c | c | c ||}
		\hline
		\multirow{7}{*}{\rotatebox{90}{ASC(0)}} & $h$ & $\errlTwo{0}$ & ${\rho_p}$ & $\errInf{0}$
                & $\varepsilon^{l_2}_0$ & $\rho_u$ \\ %& $\varepsilon^\infty_0$ \\
		\cline{2-7}
		& $3.0\times10^{-1}$ & $2.4\times10^{-3}$ &     & $6.3\times10^{-1}$ & $6.9\times10^{-5}$ &  \\ %& $2.6\times10^{-4}$ \\
		\cline{2-7}
		& $1.5\times10^{-1}$ & $6.5\times10^{-4}$ & 2.0 & $7.0\times10^{-3}$ & $3.6\times10^{-5}$ & 0.9 \\ %&$1.6\times10^{-4} $ \\
		\cline{2-7}
		& $8.1\times10^{-2}$ & $2.6\times10^{-4}$ & 1.4 & $3.2\times10^{-3}$ & $3.4\times10^{-5}$ & 0.09 \\ %&$2.0\times10^{-3}$  \\
		\cline{2-7}
		& $4.2\times10^{-2}$ & $1.4\times10^{-4}$ & 0.9 & $2.3\times10^{-3}$ & $2.1\times10^{-5}$ & 0.73 \\ %&$1.0\times10^{-3}$  \\
		\cline{2-7}
		& $2.1\times10^{-2}$ & $3.7\times10^{-5}$ & 1.9 & $1.1\times10^{-3}$ & $1.1\times10^{-5}$ & 0.93 \\ %&$6.9\times10^{-4}$  \\
		\cline{2-7}
		& $1.0\times10^{-2}$ & $2.7\times10^{-5}$ & 0.4 & $8.6\times10^{-4}$ & $6.5\times10^{-6}$ & 0.75 \\ % &$1.8\times10^{-3}$  \\
		\hline
	\end{tabular}
	\begin{tabular}[1.1]{| c | c || c | c | c ||c | c | c || }
		\hline
		\multirow{7}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{1}$ & ${\rho}$ & $\errInf{1}$ 
                & $\varepsilon^{l_2}_1$ & $\rho_u$ \\ %& $\varepsilon^\infty_1$ \\
		\cline{2-7}
		& $3.0\times10^{-1}$ & $2.4\times10^{-3}$ & & $2.1\times10^{-3}$     &$1.2\times10^{-4}$  &  \\ %&$3.0\times10^{-4}$  \\
		\cline{2-7}
		& $1.5\times10^{-1}$ & $7.0\times10^{-4}$ & 1.9 & $1.3\times10^{-2}$ &$6.5\times10^{-5}$  & 0.88 \\ %&$8.8\times10^{-4}$  \\
		\cline{2-7}
		& $8.1\times10^{-2}$ & $2.3\times10^{-4}$ & 1.8 & $6.8\times10^{-4}$ &$3.0\times10^{-5}$  & 1.25 \\ %&$2.6\times10^{-4}$  \\
		\cline{2-7}
		& $4.2\times10^{-2}$ & $6.8\times10^{-5}$ & 1.8 & $3.2\times10^{-4}$ &$1.4\times10^{-5}$  & 1.16 \\ %&$3.2\times10^{-4}$  \\
		\cline{2-7}
		& $2.1\times10^{-2}$ & $2.0\times10^{-5}$ & 1.8 & $1.1\times10^{-4}$ &$5.0\times10^{-6}$  & 1.48 \\ %&$2.4\times10^{-4}$  \\
		\cline{2-7}
		& $1.0\times10^{-2}$ & $5.4\times10^{-6}$ & 1.9 & $3.3\times10^{-5}$ &$2.2\times10^{-6}$  & 1.18 \\ %&$1.2\times10^{-4}$  \\
		\hline
	\end{tabular}
\end{table}

%% \begin{table}[h!]
%% 	\centering
%% 	\caption{Piecewise quadratic example, two materials: convergence \label{tab:conv:pwquad2_flux}}
%% 	\footnotesize
%% 	\begin{tabular}[1.1]{| c | c || c | c || c |}
%% 		\hline
%% 		\multirow{7}{*}{\rotatebox{90}{ASC(0)}} & $h$ & $\errlTwo{0}$ & ${\rho}$ & $\errInf{0}$ \\
%% 		\cline{2-5}
%% 		& $3.0\times10^{-1}$ & $9.3\times10^{-5}$ & & $2.6\times10^{-4}$ \\
%% 		\cline{2-5}
%% 		& $1.5\times10^{-1}$ & $4.2\times10^{-5}$ & & $1.6\times10^{-4}$ \\
%% 		\cline{2-5}
%% 		& $8.1\times10^{-2}$ & $4.6\times10^{-5}$ & & $2.0\times10^{-3}$ \\
%% 		\cline{2-5}
%% 		& $4.2\times10^{-2}$ & $2.5\times10^{-5}$ & & $1.1\times10^{-3}$ \\
%% 		\cline{2-5}
%% 		& $2.1\times10^{-2}$ & $1.4\times10^{-5}$ & & $6.9\times10^{-4}$ \\
%% 		\cline{2-5}
%% 		& $1.0\times10^{-2}$ & $8.9\times10^{-6}$ & & $1.8\times10^{-3}$ \\
%% 		\hline
%% 	\end{tabular}
%% 	\begin{tabular}[1.1]{| c | c || c | c || c |}
%% 		\hline
%% 		\multirow{7}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{1}$ & ${\rho}$ & $\errInf{1}$ \\
%% 		\cline{2-5}
%% 		& $3.0\times10^{-1}$ & $1.4\times10^{-4}$ &     & $3\times10^{-4}$ \\
%% 		\cline{2-5}
%% 	        & $1.5\times10^{-1}$ & $7.9\times10^{-5}$ & & $8.7\times10^{-4}$ \\
%% 		\cline{2-5}
%% 		& $8.1\times10^{-2}$ & $4.0\times10^{-5}$ & & $2.6\times10^{-4}$ \\
%% 		\cline{2-5}
%% 		& $4.2\times10^{-2}$ & $1.8\times10^{-5}$ & & $3.2\times10^{-4}$ \\
%% 		\cline{2-5}
%% 		& $2.1\times10^{-2}$ & $6.4\times10^{-6}$ & & $2.3\times10^{-4}$ \\
%% 		\cline{2-5}
%% 		& $1.0\times10^{-2}$ & $2.7\times10^{-6}$ & & $1.2\times10^{-4}$ \\
%% 		\hline
%% 	\end{tabular}
%% \end{table}

The norms of the errors are shown in Table~\ref{tab:conv:pwquad2}. ASC(1) demonstrates convergence with the rate in the $\lTwo$-norm close to quadratic for scalar unknowns and
even higher than linear for flux errors. It is important to take into accont that approximation errors in the interface reconstruction
may  effect the convergence of discretization methods. For example, in these set of tests ASC(0) convergence rate fluctuates significantly for both scalar and flux errors.
We also observe a bump in the max norm error for ASC(1) on the second mesh level, $h = 1.5\times10^{-1}$.
To have some insight, we show the corresponding mesh in the Figure~\ref{fig:conv:pwquad2:inf:mesh}.
One may note that the interface reconstruction produces significant discontinuity of interfaces:
A small volume of the external material, i.e. the one occupying $\Omega_2$ domain, appears inside the disk (domain $\Omega_1$).
Due to constant trace approximation, ASC(0) is not sensitive to such irregularity.
It turns out that for ASC(1) the $\ell^\infty$ norm of the error is affected by the appearance of such small isolated cut cells.
At the same time, this does not affect the $\lTwo$-convergence of ASC(1).

@@

%\clearpage
